### 2019-12-22 README.Rmd
Updates for website
Add tic setup files
Update travis...
Update readme

<!-- badges: start -->
<!-- badges: end -->

@@

``` r
# install.packages("devtools")
devtools::install_github("robinlovelace/zonebuilder")
```

@@

```{r}
qtm(zb_zone(x))
```

@@

```{r}
z = zb_zone(x)
tm_shape(z) +
  tm_polygons(col = "circle_id", legend.show = FALSE, palette = "magma") + 
  tm_text("label")
```

>>>>

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/zonebuilders/zonebuilder.svg?branch=master)](https://travis-ci.org/zonebuilders/zonebuilder)
<!-- badges: end -->

@@

```{r install-gh}
# install.packages("devtools")
devtools::install_github("robinlovelace/zonebuilder")
```

@@

```{r}
library(zonebuilder)
x = zb_region
z = zb_zone(x)
z
qtm(z)
```

@@

```{r}
z = zb_zone(x, n_circles = 4)
tm_shape(z) +
  tm_polygons(col = "circle_id", legend.show = FALSE, palette = "magma") + 
  tm_text("label")
```
